### 2021-10-28 src-latex/main-paper.tex
Setup paper structure

\begin{document}
%
\title{A Benchmark of Named Entity Recognition Approaches in Historical Documents\\
Application to 19$^{th}$ Century French Directories%
\thanks{This work was supported by the French National Research Agency:
Project SoDuCo, grant ANR-18-CE38-0013. ???FIXME need acknowledgments for directory sources???}}
%
\titlerunning{A Benchmark of NER Approaches in Historical Documents}
%
\author{LISTE PROVISOIRE PAR ORDRE ALPHA\\
%
Nathalie Abadie\inst{1}\orcidID{0000-1111-2222-3333} \and
Edwin Carlinet\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Joseph Chazalon\inst{3}\orcidID{2222--3333-4444-5555} \and
Bertrand Duménieu\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{INST, CITY, COUNTRY \and
INST, CITY, COUNTRY\\
\email{example@example.com}\\
\url{https://www.example.com} \and
INST, CITY, COUNTRY\\
\email{example@example.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
we use spacy \mcite{spacy}

>>>>

\begin{document}
%
\title{A Benchmark of Named Entity Recognition Approaches in Historical Documents\\
Application to 19$^{th}$ Century French Directories%
% FIXME "19$^{th}$-Century" with dash?
\thanks{This work was supported by the French National Research Agency:
Project SoDuCo, grant ANR-18-CE38-0013. ???FIXME need acknowledgments for directory sources???}}
%
\titlerunning{A Benchmark of NER Approaches in Historical Documents}
%
\author{LISTE PROVISOIRE PAR ORDRE ALPHA\\
%
Nathalie Abadie\inst{1}\orcidID{0000-1111-2222-3333} \and
Edwin Carlinet\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Joseph Chazalon\inst{3}\orcidID{2222--3333-4444-5555} \and
Bertrand Duménieu\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{INST, CITY, COUNTRY \and
INST, CITY, COUNTRY\\
\email{example@example.com}\\
\url{https://www.example.com} \and
INST, CITY, COUNTRY\\
\email{example@example.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{parts/00-abstract.tex}
\keywords{Historical documents \and Natural Language Processing \and Named Entity Recognition \and OCR noise \and Annotation cost.}
\end{abstract}

% ---- Sections ----
\input{parts/10-introduction.tex}
\input{parts/20-related-work.tex}
\input{parts/30-dataset.tex}
\input{parts/40-ner-approaches.tex}
\input{parts/50-xp-setup.tex}
\input{parts/60-results.tex}
\input{parts/80-conclusion.tex}

### 2021-10-28 src-latex/parts/10-introduction.tex
Setup paper structure

% !TeX root = ../main-paper.tex
The paper features a comparison of a selection of named entity recognition (NER) techniques which can be reasonably used in the context of historical document analysis.
Such natural language processing techniques identify which class each text token belong to, like "person name", "location", "number" or "activity".
Introducing a new public dataset built from 19th century French directories, 
we perform a practical assessment of the accuracy of, and the annotation cost (considering various training set sizes) needed by each technique.
We also study the impact of real OCR noise for several OCR systems on the performance of NER.
Experiments suggest that FIXME APPROACH NAME is the most effective approach on the dataset we processed.
All material is available freely at \url{https://github.com/soduco/paper-ner-bench-das22} and the latest version of is paper can be obtained at \url{TODO arxiv URL}.

>>>>

% !TeX root = ../main-paper.tex
\section{Introduction}
